A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2014-10-24 foreground_delay_spectrum_modeling.tex
Minor change from 170 m to 171 m for a baseline length

We also note that increasing the antenna spacing results in progressively improving the resolution along the delay axis by increasing the number of delay bins inside the {\it foreground wedge}. This improves the localization of foreground objects whose signatures are imprinted in the delay spectrum. For instance, there is an increase in the number of secondary peaks in the delay spectrum between zero--delay and horizon delay limits as the antenna spacing increases from $\sim$84~m to $\sim$170~m. In this case, these correspond to secondary lobes of the power--pattern that lie between the primary lobe and the horizon along the local meridian. At short antenna spacings, due to relatively lower resolution along the delay axis inside the {\it foreground wedge} and a consequent loss of localization of foreground emission, these secondary peaks blend in with other major peaks and are not distinctly visible. These findings are consistent with the discussion in \S\ref{sec:compact}.

In summary, the brightest signature ($\gtrsim 10^{10}$~Jy~Hz) is that of the Galactic center in the {\it off--zenith} pointing co--located at a westward secondary lobe with a significantly high gain. The next brightest signature ($\sim 10^8$--$10^9$~Jy~Hz) is caused by compact emission appearing to be concentrated in the inner regions of the {\it foreground wedge} (near zero delays) rather than towards the boundaries. Diffuse emission co--located at the primary lobe of the power--pattern is fainter by approximately an order of magnitude relative to compact emission from the same region for a $\sim 84$~m antenna spacing. But unlike the latter, diffuse emission decreases rapidly by over two orders of magnitude as the antenna spacing is widened to $\sim 170$~m. However, diffuse emission is significantly higher near horizon delay limits compared to that in the primary lobe of the power--pattern as the antenna spacing is increased. This leads to edge--heavy features in the delay spectrum. Complemented by the center-heavy compact foreground features, we predict the presence of a {\it three--pronged pitchfork}--shaped signature in the delay spectrum of the foreground sky. We identify evidence for presence of this signature in actual MWA data, although deeper observations are needed to more clearly reveal the effect.

>>>>

We also note that increasing the antenna spacing results in progressively improving the resolution along the delay axis by increasing the number of delay bins inside the {\it foreground wedge}. This improves the localization of foreground objects whose signatures are imprinted in the delay spectrum. For instance, there is an increase in the number of secondary peaks in the delay spectrum between zero--delay and horizon delay limits as the antenna spacing increases from $\sim$84~m to $\sim$171~m. In this case, these correspond to secondary lobes of the power--pattern that lie between the primary lobe and the horizon along the local meridian. At short antenna spacings, due to relatively lower resolution along the delay axis inside the {\it foreground wedge} and a consequent loss of localization of foreground emission, these secondary peaks blend in with other major peaks and are not distinctly visible. These findings are consistent with the discussion in \S\ref{sec:compact}.

In summary, the brightest signature ($\gtrsim 10^{10}$~Jy~Hz) is that of the Galactic center in the {\it off--zenith} pointing co--located at a westward secondary lobe with a significantly high gain. The next brightest signature ($\sim 10^8$--$10^9$~Jy~Hz) is caused by compact emission appearing to be concentrated in the inner regions of the {\it foreground wedge} (near zero delays) rather than towards the boundaries. Diffuse emission co--located at the primary lobe of the power--pattern is fainter by approximately an order of magnitude relative to compact emission from the same region for a $\sim 84$~m antenna spacing. But unlike the latter, diffuse emission decreases rapidly by over two orders of magnitude as the antenna spacing is widened to $\sim 171$~m. However, diffuse emission is significantly higher near horizon delay limits compared to that in the primary lobe of the power--pattern as the antenna spacing is increased. This leads to edge--heavy features in the delay spectrum. Complemented by the center-heavy compact foreground features, we predict the presence of a {\it three--pronged pitchfork}--shaped signature in the delay spectrum of the foreground sky. We identify evidence for presence of this signature in actual MWA data, although deeper observations are needed to more clearly reveal the effect.
